\section{Lightfront Hamiltonians}
\label{subsec:lightfront-hamiltonian}

Here, the Yukawa and $\phi^4$ Hamiltonians will be written out in lightfront coordinates in one space ($x^-$) and one time ($x^+$) dimension.
In the continuum, the Hamiltonian, which is derived from the Lagrangian, can be written as integrals of the relevant fields over longitudinal momentum. 
In the discrete case, the momentum is discretized, and thus integrals become sums.
Each model will have a different $\mathcal{H}$, depending on the fields involved and the interaction term.

Each model is composed of fields with discrete momenta $k \in \{1/2, 3/2, \dots\}$ for fermions or $k \in \{1, 2, 3, \dots\}$ for bosons due to their symmetry properties. 
The discretized fields are given as:

\begin{equation}
    \label{eq:psi_discrete}
    \psi(q) = 2L \frac{\theta(k)u(p_k^+)b_k+ \theta(-k)v(p_{-k}^+)d_{-k}^\dagger}{\sqrt{4\pi \abs{k}}}
\end{equation}
\begin{equation}
    \label{eq:psibar_discrete}
    \bar \psi(q) = 2L \frac{\theta(k)\bar u(p_k^+)b_k^\dagger + \theta(-k)\bar v(p_{-k}^+)d_{-k}}{\sqrt{4\pi \abs{k}}}
\end{equation}
\begin{equation}
    \label{eq:phi_discrete}
    \phi(x) = 2L \frac{\theta(k)a_k + \theta(-k)a_{-k}^\dagger}{\sqrt{4\pi \abs{k}}}
\end{equation}
The discretized momentum is given by $p_k^+ = \frac{2\pi}{L}k$. 
In the discretized Hamiltonians below, the momentum sums run to a value $K$, known as the \textit{resolution}.
This is analogous to the mode cutoff discribed throughout the text. 
Increasing the resolution $K$ recovers the continuum limit.

The spinors $u, v$ and gamma matrices $\gamma^+$ have the following definitions in 1+1D lightfront coordinates:

\begin{align*}
    u(p_k^+) = \frac{1}{\sqrt{p_k^+}}\left[\begin{matrix} p^+ \\ m \end{matrix}\right]\\
    v(p_k^+) = \frac{1}{\sqrt{p_k^+}}\left[\begin{matrix} -p^+ \\ m \end{matrix}\right]\\
    \gamma^+ = \left[\begin{matrix} 0 & 1 \\ 1 & 0 \end{matrix}\right]
\end{align*}


\subsection{Yukawa}
In the Yukawa model, the discrete Hamiltonian is a sum of three terms: $H = H_0 + H_{\text{3-point}} + H_{\text{inst.}}$.
The free part of the Hamiltonian is 

\begin{equation}
    H_0 = \frac{L}{2\pi}\sum_{k = 1/2}^K \frac{m_f^2}{p_k^+}\left(b_k^\dagger b_k + d_k^\dagger d_k \right) + \frac{L}{2\pi}\sum_{k = 1}^K \frac{m_b^2}{p_k^+}a_k^\dagger a_k 
\end{equation}

The 3-body interaction piece comes from a sum over the fields $\bar \psi \psi \phi$:

\begin{equation}
    H_{\text{3-body}} = \frac{2Lg}{(2L)^3}\sum_{\substack{k_1, k_2 \in \mathbb{Z} + \frac{1}{2} \\ k_3 \in \mathbb{Z} \setminus \{0\}}}
    \delta_{k1, k2 + k3}:\bar \psi(k_1)\psi(k_2)\phi(k_3):.
\end{equation}

Lastly, the instantaneous interaction, arising from constraints on the spinor fields in lightfront coordinates can be written in terms of fields as:
\begin{equation}
    H_{\text{inst.}} = \frac{2Lg^2}{(2L)^4}\sum_{\substack{k_1, k_4 \in \mathbb{Z} + \frac{1}{2} \\ k_2, k_3 \in \mathbb{Z} \setminus \{0\}}}
    \delta_{k1, k2 + k3 + k4}:\bar \psi(k_1)\phi(k_2)\frac{\gamma^+}{k_3 + k_4}\phi(k_3)\psi(k_4):.
\end{equation}

The explicit form of these Hamiltonians written in the manner of equation \ref{eq:lco} can be found by expanding the fields in the forms found above.

\subsection{$\phi^4$}
The $\phi^4$ Hamiltonian can be written out in lightfront coordinates, similar to Yukawa theory. Using the same field given in equation \ref{eq:phi_discrete}, the discrete Hamiltonian is


\begin{align}
    H = 
\sum_{k_1 = 1}^{K} \frac{m_B^2}{p_{k_1}^+} a_1^\dagger a_1
&+
4 g
\frac{1}{2L} \sum_{k_1, k_2, k_3, k_4 = 1}^{K}
\frac{1}{\sqrt{p_{k_1}^+ p_{k_2}^+ p_{k_3}^+ p_{k_4}^+}}
\delta_{k_1 + k_2 + k_3, k_4}
\left(
  a_1^\dagger a_2^\dagger a_3^\dagger a_4
+ a_4^\dagger a_3 a_2 a_1
\right)
\\ 
& +6 g
\frac{1}{2L} \sum_{k_1, k_2, k_3, k_4 = 1}^{K}
\frac{1}{\sqrt{p_{k_1}^+ p_{k_2}^+ p_{k_3}^+ p_{k_4}^+}}
\delta_{k_1 + k_2, k_3 + k_4}
a_1^\dagger a_2^\dagger a_3 a_4 \\ \nonumber
\end{align}