\section{Results}
\label{sec:results}

In this section, we numerically evaluate the quantum resources required for block-encoding various operators using LOBE.
The spacetime costs that we analyze include: the number of T gates, the number of non-Clifford single qubit rotations, the number of block-encoding ancillae, the maximum number of qubits required, and the rescaling factor imposed on the resulting block-encoding.

We compare the LOBE constructions presented in Section \ref{sec:ladder-op-oracles} to techniques that first expand the ladder operators in the Pauli basis and then block-encode the resulting linear combinations of Pauli operators using LCU.
The Jordan-Wigner transformation \cite{jordan-wigner} is used to expand fermionic ladder operators in the basis of Pauli operators, while the Standard Binary encoding \cite{standard-binary} is used to expand bosonic ladder operators.

The first Pauli-based method we compare against will be referred to as ``Pauli Expansion''.
In this method, the respective Pauli transformations are applied to the ladder operators and fully expanded, resulting in a single linear combination of Pauli operators.
This linear combination, which describes the full operator, is then block-encoded using the LCU framework.

The second Pauli-based method we compare against will be referred to as ``Piecewise Pauli''.
In this method, each product of ladder operators acting on a single mode is expanded in the Pauli basis and then block-encoded using the LCU framework.
These block-encodings of the ladder operators acting on each mode are then combined together to produce a block-encoding of the full operator using the techniques described in subsections \ref{subsec:lco} and \ref{subsec:be-products}.

In the following subsections, we benchmark these three different block-encoding methods for various types of operators.
First, we analyze the associated spacetime costs for block-encoding several classes of operators which appear in many second-quantized models.
Then, we present the spacetime costs for block-encoding Hamiltonians associated with various models that arise in quantum field theory.
These models include Hamiltonians derived from two non-relativistic models - the quartic harmonic oscillator and the static massive Yukawa - and two fully relativistic models - $\phi^4$ theory and the full massive Yukawa.

For all block-encodings, we will assume that all terms are mode ordered (Eq. \ref{eq:mode-ordered}) and that the identity term is removed.
The identity term is removed since it artificially inflates the rescaling factor and only results in a constant shift in the spectrum of the Hamiltonian, however, if required it can be included with a negligible increase in spacetime quantum resources.

The results presented in this section are generated using a software library called LOBE which has been made open-source \cite{}.
The circuits are implemented using Cirq \cite{cirq} and block-encodings are numerically verified for circuits of up to 18 qubits.
OpenParticle \cite{openparticle}, a software library for the construction and manipulation of fermionic, antifermionic, and bosonic ladder operators, is used to define the operators.
The Symmer software library \cite{} is also used for various subroutines, including, but not limited to, expanding the ladder operators in the Pauli basis.
The software library \cite{grover-rudolph-github} is used to determine the rotation angles required for arbitrary state-preparation using Grover-Rudolph.

\input{text/results/components}
\input{text/results/qosc}
\input{text/results/static_yukawa}
\input{text/results/phi4}
\input{text/results/full_yukawa}
